Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-11-15 Articles/Article 1/main.tex
minor

\add{
	-orientation error \\ 
	- p = v w \\
	- describe constants
	- shorten
}

@@

% JUST RIGHT
Our method innovatively employs a velocity profile to direct the end effector (EE) towards its target, marking a departure from Khatib's joint coordinate approach in favor of a Cartesian coordinate framework. This is particularly beneficial in scenarios involving redundant manipulators, where determining an optimal goal joint configuration in advance is challenging.

>>>>

\add{
	-orientation error \\ 
	- p = v w \\
	- shorten
}

@@

% JUST RIGHT
Our method \remove{innovatively} employs inverse kinematics approach (IK) to guide the end effector (EE) towards its target, marking a departure from Khatib's joint coordinate approach in favor of a Cartesian coordinate framework. This is particularly beneficial in scenarios involving redundant manipulators, where determining an optimal goal joint configuration in advance is challenging.
